---
title: "Data_Mining_Project"
author: "Raphael"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Loading Libraries

```{r}
library(MASS)
library(ISLR2)
library(car)

```

## Loading Boston Data set 
```{r}
head(Boston)

```
```{r}
?Boston
```

# To build model and attach data

```{r}
 lm.fit <-lm(medv~lstat, data = Boston)
 attach(Boston)
 lm.fit <-lm(medv~lstat)

```

# to get model fit


```{r}
lm.fit
```
```{r}
summary(lm.fit)
```

```{r}
# names of  other information stored in model
names(lm.fit)
# To get coefficient

coef(lm.fit)
# To get CI

confint(lm.fit)
# To do prediction
predict(lm.fit, data.frame(lstat = (c(5, 10, 15))),
interval = "confidence")
# 
predict(lm.fit, data.frame(lstat = (c(5, 10, 15))),
interval = "prediction")

```

```{r}
# We will now plot medv and lstat along with the least squares regression
#line using the plot() and abline() functions

 plot(lstat, medv)
 abline(lm.fit)
```
# There is some evidence for non-linearity in the relationship between lstat
# and medv.

```{r}
 plot(lstat, medv)
 abline(lm.fit)
 abline(lm.fit, lwd = 3)
 abline(lm.fit, lwd = 3, col = "red")
 plot(lstat, medv, col = "red")
 plot(lstat, medv, pch = 20)
 plot(lstat, medv, pch = "+")
 plot(1:20, 1:20, pch = 1:20)
```

# Diagnostic plots 

```{r}
par(mfrow = c(2, 2))
plot(lm.fit)
```

# we can compute the residuals from a linear regression fit
# using the residuals()
```{r}
plot(predict(lm.fit), residuals(lm.fit))
plot(predict(lm.fit), rstudent(lm.fit))
```

# Plot for residual plots

```{r}
plot(hatvalues(lm.fit))
which.max(hatvalues(lm.fit))
```
# Multiple Linear Regression

```{r}
lm.fit <- lm(medv~ lstat + age, data = Boston)
 summary(lm.fit)
```
# Multiple regression of all predictors

```{r}
lm.fit <-lm(medv~., data = Boston)
summary(lm.fit)
```
# VIF
```{r}
vif(lm.fit)
```
# Running model with no un significant variable

```{r}
 lm.fit1 <-lm(medv~.- age, data = Boston)
 summary(lm.fit1)
```
# or use  update ()

```{r}
 lm.fit1 <-update(lm.fit,~.- age)
 summary(lm.fit1)
```
# InteractionTerms

```{r}
summary(lm(medv~lstat * age, data = Boston))
```
# Non-linearTransformations of the Predictors

```{r}
lm.fit2 <-lm(medv~lstat + I(lstat^2))
 summary(lm.fit2)
```


